Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
spell
Nit in IV

In the case of single packet tail loss, the last outstanding packet is sent as probe and in case of n-degree tail loss, the latest packet is sent 
as probe to trigger fast retransmit of the packets in between. In order to observe the performance of n-degree tail loss, we consider dropping the 
last two packets. The results of two packet tail loss are shown in Figure~\ref{2p}. In this case, TLP performs better than the RTO 
setting in all scenarios except when packets are lost on a high delay interface. In this scenario, the MPTCP retransmission follows the 
behavior depicted in Figure~\ref{timing2P} and the delay difference is large enough that the retransmission of the last packet on the alternate 
path is faster than the probe on the primary path.

>>>>

In the case of single packet tail loss, the last outstanding packet is sent as probe and in case of n-degree tail loss, the latest packet is sent 
as probe to trigger fast retransmit of the packets in between. In order to observe the performance of n-degree tail loss, we consider dropping the 
last two packets. The results of two packet tail loss are shown in Figure~\ref{2p}. In this case, TLP performs better than the RTO 
setting in all scenarios except when packets are lost on a high delay interface. In this scenario, the MPTCP retransmission follows the 
behavior depicted in Figure~\ref{timing2P} and the delay difference is large enough that the retransmission of the last packet on the alternate 
path is faster than the probe on the original path.
